\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{ragged2e}
\usepackage{hyperref}



%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{10in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.5in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Micah Dameron} & \textbf{\today} \\
Program Manager | Technical Writer & micahdameron@gmail.com \\
18184 Swiss Dr|Spring Lake MI, 49456 &  github.com/chronaeon \\
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	
	\item \ressubheading{ConsenSys Diligence}{Remote, USA}{Program Manager | Documentation, Content, \& Community}{May 2018 - January 2019}
	
	\begin{itemize}
		\resitem{Author and document shellcode to unify tooling and automate system-level security auditing processes.}
		\resitem{Build and document Odyssey, our audit report generation tool written in Ruby.}
		\resitem{Curate and document process description for performing a security audit.}
		\resitem{Collaborate remotely to establish and act on team goals using Zoom, E-Mail, Slack, Trello, Confluence, and Jira.}
		\resitem{Manage, compile, and print the \textbf{Diligence Handbook}, designing it to invoke and inspire shared culture.}
		\resitem{Curate and contribute public-facing posts to the Diligence Medium publication.}
	\end{itemize}
	
\end{itemize}

\begin{itemize}

	\item \ressubheading{ConsenSys}{Remote, USA}{Technical Scribe | Beigepaper Author}{August 2017 - May 2018}

\begin{itemize}
        \resitem{Transcribe technically dense business meetings for Joe Lubin, ConsenSys' founder.}
    	\resitem{Communicate clearly with team regarding scheduling, goals, and distribution of meeting notes.}
		\resitem{Transform the content of Ethereum's Yellowpaper into the \textbf{Beigepaper}, promoting readability. \\  \url{https://www.github.com/chronaeon/beigepaper.git}}
		\resitem{Write public-facing introductory blogs on crypto-economics \& related topics.}

\end{itemize}

\end{itemize}

\begin{itemize}

	\item \ressubheading{ConsenSys}{Brooklyn, USA}{Intern | Alethio}{Summer 2017}

\begin{itemize}
	\resitem{Use Git to clone, commit, push, and discuss granular changes to definitions in The Ethereum Ontology \url{https://www.github.com/ConsenSys/EthOn.git}.} 
	\resitem{Create weekly reports for the team summarizing my work activities.}
	\resitem{Locate and correlate significant events on the Ethereum Blockchain and add their description in the ontology.}
	\resitem{Write a report on best practices for creating \textit{Specialized Online Dictionaries}}.
	\resitem{\textbf{Accomplishments:}}
		\begin{itemize}
				\resitem{Hackathon Team Implements ERC-20 Token Standard in \textit{Viper}}
		\end{itemize}
\end{itemize}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
	\resitem{Able to Express complex ideas in generally understandable prose.}
	\resitem{Proficient in Bash, Linux, C, \LaTeX, TiKz HTML, et al.}
	\resitem{Able to interact meaningfully with, think about, and write about burgeoning Blockchain research topics including emerging philosophies, crypto-economics, mechanism design, and security issues.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\ressubheading{Coursera}{Remote, USA}{Data Science Certification (In Progress)}{2018-2019} 
\end{itemize}

\begin{itemize}
	\ressubheading{Front Range Community College}{Longmont, USA}{Precision Machining Technology}{2014-2016}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\resheading{Hackathon Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\vspace{-2pt}
%	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
%		\multicolumn{2}{c}{\textsc{ConsenSys Intern Hackathon:} \textit{Most Value Added to Ecosystem in 30 Hours} \cftdotfill{\cftdotsep} \textit{2017}} \\
%		\vphantom{E}
%\end{tabular*}
%\end{center}\vspace*{-16pt}
\resheading{References}
\begin{itemize}
	\resitem{\textbf{Tom Lindeman}: BizDev \& Strategy | ConsenSys Diligence | tom.lindeman@consensys.net}
	\resitem{\textbf{Maggie Colgan}: Technical Scribe | ConsenSys | maggie.colgan@consensys.net}
\end{itemize}


\end{document}
